\begin{thebibliography}{00}
\bibitem{cao2018} Cao, Q., Shen, L., Xie, W., Parkhi, O.M., \& Zisserman, A. 
(2018). Vggface2: A dataset for recognising faces across pose and age. In 2018 
13th IEEE international conference on automatic face \& gesture recognition 
(FG 2018) (pp. 67–74). IEEE.
\bibitem{parkhi2015} Parkhi et al. 2015 - Parkhi, O. M., Vedaldi, A., \& 
Zisserman, A. (2015). Deep face recognition. In BMVC (Vol. 1, p. 6).
\bibitem{sun2014} Sun et al. 2014; - Sun, Y., Chen, Y., Wang, X., \& Tang, X. 
(2014). Deep learning face representation by joint identification–verification. 
In Advances in neural information processing systems (pp. 1988–1996).
\bibitem{taigman2014} Taigman et al. 2014 - Taigman, Y., Yang, M., Ranzato, M., 
\& Wolf, L. (2014). Deepface: Closing the gap to human-level performance in face 
verification. In Proceedings of the IEEE conference on computer vision and 
pattern recognition (pp. 1701–1708).
\bibitem{pumarola2020} Pumarola, A., Agudo, A., Martinez, A.M. et al. 
GANimation: One-Shot Anatomically Consistent Facial Animation. Int J Comput Vis 
128, 698–713 (2020). 
\bibitem{suit} Suit, J. Generating Facial Expressions
\bibitem{chen2018} Chen, Mingyi \& Li, Changchun \& Li, Ke \& Zhang, Han \& He, 
Xuanji. (2018). Double Encoder Conditional GAN for Facial Expression Synthesis. 
9286-9291. 10.23919/ChiCC.2018.8483579. 
\bibitem{choi2018} Choi, Y., Choi, M., Kim, M., Ha, J.W., Kim, S., Choo, J.: 
Stargan: Unified generative adversarial networks for multi- domain 
image-to-image translation. CVPR (2018)
\bibitem{pumarola2018} Pumarola, A., Agudo, A., Martinez, A.A., Sanfeliu, A., 
Moreno-Noguer, F.: Ganimation: Anatomically-aware facial animation from a single
image. In: ECCV (2018)

% exp results
\bibitem{kingma2014} Kingma, Diederik \& Ba, Jimmy. (2014). Adam: A Method for 
Stochastic Optimization. International Conference on Learning Representations. 
\end{thebibliography}
    